Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and music aural skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-04-11 MasterThesis.tex
Updates from Overleaf

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{fadings}
\usetikzlibrary{positioning}

>>>>

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{fadings}
\usetikzlibrary{matrix, positioning}

%---NN tikz diagrams---

\usepackage{amsmath} % for aligned
%\usepackage{amssymb} % for \mathbb
\usepackage{tikz}
%\usepackage{etoolbox} % for \ifthen
\usepackage{listofitems} % for \readlist to create arrays
\usetikzlibrary{arrows.meta} % for arrow size
\usepackage[outline]{contour} % glow around text
\contourlength{1.4pt}

\tikzset{>=latex} % for LaTeX arrow head
\usepackage{xcolor}
\colorlet{myred}{red!80!black}
\colorlet{myblue}{blue!80!black}
\colorlet{mygreen}{green!60!black}
\colorlet{myorange}{orange!70!red!60!black}
\colorlet{mydarkred}{red!30!black}
\colorlet{mydarkblue}{blue!40!black}
\colorlet{mydarkgreen}{green!30!black}
\tikzstyle{node}=[thick,circle,draw=myblue,minimum size=22,inner sep=0.5,outer sep=0.6]
\tikzstyle{node in}=[node,green!20!black,draw=mygreen!30!black,fill=mygreen!25]
\tikzstyle{node hidden}=[node,blue!20!black,draw=myblue!30!black,fill=myblue!20]
\tikzstyle{node convol}=[node,orange!20!black,draw=myorange!30!black,fill=myorange!20]
\tikzstyle{node out}=[node,red!20!black,draw=myred!30!black,fill=myred!20]
\tikzstyle{connect}=[thick,mydarkblue] %,line cap=round
\tikzstyle{connect arrow}=[-{Latex[length=4,width=3.5]},thick,mydarkblue,shorten <=0.5,shorten >=1]
\tikzset{ % node styles, numbered for easy mapping with \nstyle
  node 1/.style={node in},
  node 2/.style={node hidden},
  node 3/.style={node out},
}
\def\nstyle{int(\lay<\Nnodlen?min(2,\lay):3)} % map layer number onto 1, 2, or 3

%------------------------

### 2023-04-11 introduction/Subsections/Objectives.tex
Updates from Overleaf

\begin{enumerate}
\item Music recommendation: The learned embedding space can retrieve similar musical content and recommend songs or playlists to users based on their listening history or preferences.
\item Music classification: The embedding space can classify songs based on genre, mood, or other musical characteristics.
\item Music transcription: The learned embedding space can transcribe audio signals into symbolic music notation, such as MIDI or sheet music.
\item Music generation: The embedding space can generate new musical content by sampling from the learned distribution of musical features.
\item Music synchronization: The learned embedding space can synchronize audio and visual content in applications such as music videos or virtual reality experiences.
\item Music search: The embedding space can search for specific musical content based on high-level perceptual concepts and the relationships they have among them
\end{enumerate}

>>>>

\begin{enumerate}
\item Music recommendation: The learned embedding space can retrieve similar musical content and recommend songs or playlists to users based on their listening history or preferences.
\item Music classification: The embedding space can classify songs based on genre, mood, or other musical characteristics.
\item Music transcription: The learned embedding space can transcribe audio signals into symbolic music notation, such as MIDI or sheet music.
\item Music generation: The embedding space can generate new musical content by sampling from the learned distribution of musical features.
\item Music synchronization: The discovered embedding space can synchronize audio and visual content in applications such as music videos or virtual reality experiences.
\item Music search: The embedding space can search for specific musical content based on high-level perceptual concepts and the relationships they have among them
\end{enumerate}

### 2023-04-11 methods/subsections/machine learning.tex
Updates from Overleaf

@@

\item \textbf{Convolutional layers:} These layers apply a convolution operation to the input data. The raw audio data can be either a 1D signal or transformed into a spectrogram or a Mel-spectrogram representation, which can be considered an image-like 2D representation of the audio data. The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation of convolution, see this video: \url{https://youtu.be/KuXjwB4LzSA}}.

\textbf{Convolution:} It involves sliding a small window, called a filter or kernel, over input data to compute the dot product between the kernel and each local region of the data. The result is a new feature map highlighting patterns and essential information.

>>>>

%Activation equation
\input{figures/neural networks/activation}

@@

\item \textbf{Convolutional layers:} These layers apply a convolution operation to the input data. The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation of convolution, see this video: \url{https://youtu.be/KuXjwB4LzSA}}.

A convolution operation involves sliding a small window, called a filter or kernel, over input data to compute the dot product between the kernel and each local region of the data. The result is a new feature map highlighting patterns and essential information.
